Gromov--Witten theory of hypersurfaces in genus one

### 2019-02-19 GenusOneRelativeMaps.tex
Finished Step 2 - it was actually fine in the end

%target
\draw [color=blue,->] (0,-1) to (2,-1);
\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
\end{tikzpicture}
\end{center}
which gives a contribution of
\begin{equation*} d\cdot \tilde\gamma \cap [\VZ_{1,(d,\underbrace{0,\ldots,0}_{n-1})}(X|Y,\beta)] \end{equation*}
to the right-hand side of \eqref{step 2 recursion}. The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor. On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
\begin{equation}\label{step 2 recursion 2} I = (-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$. We obtain a new insertion, also denoted $\tilde\gamma$, by introducing $\fgt_y^\st$ everywhere. Recursing at $x_1$ we obtain:
\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
The left-hand side is a forgetful relative invariant of degree $d$ and $n+1$ markings ($y$ being the ``forgetful'' marking), hence is recursively known. On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining markings):
\begin{center}
\begin{minipage}{0.4\textwidth}
\begin{tikzpicture}[scale=1]
%edge
\draw (0,-0.1) to (2,-0.1);
\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};

@@

\draw (2,-1.5) node[below]{\small{Case 1}};
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{tikzpicture}[scale=1]
%edge
\draw (0,0) to (2,0);
\draw [color=blue] (1,0) node[above]{\tiny$d$};

@@

\draw (2,-1.5) node[below]{\small{Case 2}};
\end{tikzpicture}
\end{minipage}
\end{center}
In Case 1 the contribution from $\sqC_1$ is a forgetful relative invariant with $\leq n+1$ markings, hence is recursively known. In Case 2, we first note that there cannot be any more markings on $\sqC_0$ (since otherwise we could apply $\fgt_y$ to conclude that the contribution vanishes). Thus we obtain a single locus, which contributes precisely
\begin{equation*} d\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = -\tilde\gamma\cap[\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)]\end{equation*}
which is the first term on the right-hand side of \eqref{step 2 recursion 2}. As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we obtain:
\begin{equation*} d^2\cdot(-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -d\cdot\gamma \cap [\VZ_{1,n}(X|Y,\beta)].\end{equation*}
Rearranging in \eqref{step 2 recursion 2} we end up with:

WHOOPS! WE'VE CANCELED OUT! NEED TO TRY HARDER.

>>>>

%target
\draw [color=blue,->] (0,-1) to (2,-1);
\draw [fill=blue,color=blue] (0,-1) circle[radius=3pt];
\draw [color=blue] (2,-1) node[right]{\small$\Sigma(X|Y)$};
\end{tikzpicture}
\end{center}
which gives a contribution of
\begin{equation*} d\cdot \gamma \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] \end{equation*}
to the right-hand side of \eqref{step 2 recursion}. Here $\gamma$ is the insertion we started with; the difference is that we are now considering relative maps with maximal tangency at $x_1$, rather than absolute maps. The type $B$ and $C^0$ loci are recursively determined as in Step~1, and similarly the type $C^+$ loci are recursively determined except for the locus where the entire curve is mapped into the divisor. On this locus we may apply $\fgt_{x_0}$ and identify the contribution with
\begin{equation*} d^2 \cdot \gamma \cap [\VZ_{1,n}(Y,\beta)] = d^2 \cdot I \end{equation*}
where $I$ is the invariant we are trying to compute. Putting this all together, we obtain
\begin{equation}\label{step 2 recursion 2} I = (-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] + \text{recursively known terms} \end{equation}
where on the right-hand side there are $n-1$ non-relative markings $x_2,\ldots,x_n$, and a relative marking $x_1$. We now apply the recursion again to the right-hand side, by considering the space
\begin{equation*} \VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta) \end{equation*}
where $x_1$ now has tangency $d-1$ and we have introduced a new marking $y$ with tangency $1$. We consider a new insertion, denoted $\tilde\gamma$ as usual, by introducing $\fgt_y^\st$ everywhere. Recursing at $x_1$ we obtain:
\begin{equation*} \left( (d-1)\psi_1 + \ev_1^\st Y \right)\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d-1,1,0,\ldots,0)}(X|Y,\beta)] = (-\tilde\gamma/d) \cap [\Dcal(1)].\end{equation*}
The left-hand side is a forgetful relative invariant of degree $d$ and $n+1$ markings ($y$ being the ``forgetful'' marking), hence is recursively known. On the right-hand side, the type $A$ loci are recursively known except possibly in the following special cases (with some stable distribution of the remaining markings):
\begin{center}
\begin{minipage}{0.4\textwidth}
\begin{tikzpicture}[scale=1]
%edge
\draw (0,-0.1) to (2,-0.1);
\draw [color=blue] (1,-0.1) node[below]{\tiny$d-1$};

@@

\draw (2,-1.3) node[below]{\small{Case 1}};
\end{tikzpicture}
\end{minipage}
\begin{minipage}{0.4\textwidth}
\begin{tikzpicture}[scale=1]
%edge
\draw (0,0) to (2,0);
\draw [color=blue] (1,0) node[above]{\tiny$d$};

@@

\draw (2,-1.3) node[below]{\small{Case 2}};
\end{tikzpicture}
\end{minipage}
\end{center}
In Case 1 the contribution from $C_1$ is a forgetful relative invariant with $\leq n$ true markings, hence is recursively known. In Case 2, we first note that there cannot be any more markings on $C_0$ (since otherwise we could apply $\fgt_y$ and conclude that the contribution vanishes). Thus we obtain a single locus, which contributes precisely
\begin{equation*} d\cdot(-\tilde\gamma/d) \cap [\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)] = -\tilde\gamma\cap[\VZ_{1,(d,0,\ldots,0)}(X|Y,\beta)]\end{equation*}
which gives us the first term on the right-hand side of \eqref{step 2 recursion 2}. As usual the type $B$ and $C^0$ contributions are known recursively, and the only type $C^+$ contribution not known recursively occurs when the entire curve is mapped into the divisor, in which case we apply $\fgt_y$ to calculate the contribution as:
\begin{equation*} (-\gamma/d) \cap [\VZ_{1,n}(X|Y,\beta)] = -I/d.\end{equation*}
Substituting into \eqref{step 2 recursion 2} we end up with
\begin{equation*} I(1-d^{-2}) = \text{recursively known terms} \end{equation*}
which completes the recursion step as long as $d \neq 1$. But since $\VZ_{1,n}(H,1)=\emptyset$ it follows that $\VZ_{1,n}(Y,\beta)=\emptyset$ if $d=Y\cdot\beta=1$, so we may always assume $d \geq 2$ in the recursion.
